### 2021-04-22 README.Rmd
fsda

If the console output instead suggests Make is not installed, the user may want to search for how they can install it (given their particular flavor of Mac or Linux). For Mac users, most paths would lead to [installing or updating Xcode from the App Store](https://stackoverflow.com/questions/10265742/how-to-install-make-and-gcc-on-a-mac) through the popular [`Homebrew` package manager](https://brew.sh) should also do this. Linux users in the Debian family (prominently: Ubuntu) who, for some reason, don't already have this installed can install it via `sudo apt-get install build-essential` or `sudo apt-get -y install make` in a console. Linux users in the Red Hat family (prominently: Fedora) should be able to install it by way of `sudo yum install yum-utils` or `dnf install @development-tools`. However, it seems impossible that these would not already be installed on most Linux distributions these days. No matter, `make -v` should confirm its presence after one of these installation paths.

@@

This will create a new directory in the working directory, titled "dissertation", that includes a skeleton of a research project to assist the user in getting started on their academic paper/project. That directory will be located in the current working directory. The only downside to the console approach over the Rstudio approach is the console approach won't create an `.Rproj` file in the directory. The Rstudio approach will.

>>>>

If the console output instead suggests Make is not installed, the user may want to search for how they can install it (given their particular flavor of Mac or Linux). For Mac users, most paths would lead to [installing or updating Xcode from the App Store](https://stackoverflow.com/questions/10265742/how-to-install-make-and-gcc-on-a-mac) though the popular [`Homebrew` package manager](https://brew.sh) should also do this. Linux users in the Debian family (prominently: Ubuntu) who, for some reason, don't already have this installed can install it via `sudo apt-get install build-essential` or `sudo apt-get -y install make` in a console. Linux users in the Red Hat family (prominently: Fedora) should be able to install it by way of `sudo yum install yum-utils` or `dnf install @development-tools`. However, it seems impossible that these would not already be installed on most Linux distributions these days (and for Mac as well). It is one of the oldest and still most widely used GNU programs. No matter, `make -v` should confirm its presence after one of these installation paths.

@@

This will create a new directory in the working directory, titled "dissertation", that includes a skeleton of a research project to assist the user in getting started on their academic paper/project. That directory will be located in the current working directory. The only downside to the console approach over the Rstudio approach is the console approach won't create an `.Rproj` file in the directory. The Rstudio approach will do this. The choice is yours whether you want this, but `.Rproj` files are wonderful for keeping environments insular in Rstudio.
